README

### 2019-05-30 Code/07_build_classifier.Rmd
Restructured the folders of the project. The folder formerly labeled as "dallin_annotations" has now become the "Code" folder. The "dallin_annotations" folder contained all of the R and python scripts in Code, but renamed and organized scripts according to the tidyverse styleguide. All other files in the folder formerly named "Code" have been deleted (they were redundant).

The scree plot shows variances (in other words, variance undescribed by the model) on the y-axis, and principal components on the x-axis. For example, with only one principal component, a large amount of variance remains in the data. With two principal components, however, we see that the amount of undescribed variance drops considerably. The rule of thumb with the scree plot is to identify the "elbow" (where the slope of the line starts to flatten out), and choose a number of principal components based on number of principal components at that point. Using this plot, for example, we will use the first four principal components of the model. Using four principal components will help us achieve a model that is both simple, and accurate. Using more than four principal components will result in significantly diminished returns -- it will slow down our model without providing a significant improvement to our model's predictive ability. 
```{r}
# make a scree plot of the components
screeplot(train.pr, type = "line", npcs = 20)

@@

### Save the Model
```{r}
# save(bst, file = here::here("Output", "xgb.modelPC4.dat"))
# xgb.save(bst, here::here("Output", "xgb.modelPC4-xgb_version.dat"))
# save(test_data, file = here::here("Output", "test_data.dat"))
```

>>>>

The scree plot shows variances undescribed by the model on the y-axis, and principal components on the x-axis. For example, with only one principal component, a large amount of variance remains in the data. With two principal components, however, we see that the amount of undescribed variance drops considerably. The rule of thumb with the scree plot is to identify the "elbow" (where the slope of the line starts to flatten out), and choose a number of principal components based on number of principal components at that point. Using this plot, for example, we will use the first four principal components of the model. Using four principal components will help us achieve a model that is both simple, and accurate. Using more than four principal components will result in significantly diminished returns -- it will slow down our model without providing a significant improvement to our model's predictive ability. 
```{r}
# make a scree plot of the components
screeplot(train.pr, type = "line", npcs = 20)

@@

### Save the Model
```{r}
# save(bst, file = here::here("Output", "xgb.modelPC4.dat"))
# xgb.save(bst, here::here("Output", "xgb.modelPC4-xgb_version.dat"))
# save(test_data, file = here::here("Output", "test_data.dat"))
save(train, file = ../../Output/train.Rdata) # Save the training file so it can be referenced in the paper
```

### 2019-05-30 Code/11_build_multi_classifier.Rmd
Restructured the folders of the project. The folder formerly labeled as "dallin_annotations" has now become the "Code" folder. The "dallin_annotations" folder contained all of the R and python scripts in Code, but renamed and organized scripts according to the tidyverse styleguide. All other files in the folder formerly named "Code" have been deleted (they were redundant).

# Overview
In this document, I will try to make a classification model similar to the one in 07_build_classifier.Rmd. The difference here will be that I will attempt to build a classification model meant to predict based on a set of many complaint categories.

@@

## Load the Training Dataset
This dataset was created in file 07_build_classifier.Rmd. This dataset contains tweets that have been processed by unsupervised models (a fastText word embeddings model, and a PCR model trained on the fastText word embeddings). These unsupervised models were trained on millions of tweets instead of a few thousand, so we expect them to perform well on phrases and words that were not included in the relatively small labeled training dataset of a few thousand tweets.
```{r}
load(here::here("Output", "train_data.dat"))
```

@@

Accuracy of non-complaint predictions:
```{r}
test_data %>% 
  filter(complaint_category != 1) %>% 
  summarise(mean(correct))
```
It appears that when predicting non-complaints, the model is only accurate about 25% of the time. This is very poor, but better than rolling the dice.

>>>>

# Overview
In this document, I will try to make a classification model similar to the one in 07_build_classifier.Rmd. The difference here will be that the classification model will predict based on a set of several complaint categories.

@@

## Load the Training Dataset
This dataset was created in file 07_build_classifier.Rmd. This dataset contains tweets that have been processed by unsupervised models (a fastText word embeddings model, and a PCR model trained on the fastText word embeddings). These unsupervised models were trained on millions of tweets instead of a few thousand, so we expect them to perform well on phrases and words that were not included in the relatively small labeled training dataset of about five thousand tweets.
```{r}
load(here::here("Output", "train_data.dat"))
```

@@

Accuracy of non-complaint predictions:
```{r}
test_data %>% 
  filter(complaint_category != 1) %>% 
  summarise(mean(correct))
```
It appears that when predicting non-complaints, the model is only accurate about 25% of the time. This is very poor, but better than rolling the dice. Regardless, I wouldn't put a lot of trust in its predictions.

### 2019-05-30 Code/README.Rmd
Restructured the folders of the project. The folder formerly labeled as "dallin_annotations" has now become the "Code" folder. The "dallin_annotations" folder contained all of the R and python scripts in Code, but renamed and organized scripts according to the tidyverse styleguide. All other files in the folder formerly named "Code" have been deleted (they were redundant).

---
title: "Code"
output: github_document
---

## Description

Each script should do something specific (like tidyverse functions), have a descriptive name, and include number prefixes if they are meant to be run in a certain order (e.g., `01_import_data.R`, `02_clean_data.R`).

## Project Workflow

* Use RStudio projects.
* Use `here::here()` to specify files paths.
* Use tidyverse functions as much as possible.
* Try and follow the [tidyverse style guide](https://style.tidyverse.org).

>>>>

---
title: "README"
output: github_document
---
# Dallin Annotations
In this folder, I will keep all of my .rmd documents. Some of them will be created by me, but most will take Adriel's code in other folders and annotate it. I hope that by doing so, I will better understand his code, and be able to contribute more to writing the paper on our reasearch. Additionally, I hope these annotations help future RA's understand the code as well.

The numbering of the files is an attempt to be consistent with the tidyverse style guide section 1.1 (found at https://style.tidyverse.org/). As I work more with the code, I will do my best to ensure that the numbering reflects a logical flow for the code.

If the documents only contain a single, massive block of code, this means that I haven't gotten around to annotating that script.

Below, I have a quick and brief documentation of what I understand about each file.

# Overview of Files
Note: Files prefaced by 99_ are files that I don't understand completely, and seem to be more related to data wrangling than model building.

### 01_test_rds_connection.R
This file contains the credentials necessary to log into the R Data Server. It also has brief code for extracting some of the tweets from the database, and it writes the data to a .txt file.

### 02_visualize_twitter_data.R
This file takes airline twitter data and creates a few visualizations (i.e. wordclouds) on the tweet text. It was formerly called CountingCockroaches.R.

### 03_analyze_complaint_categories.Rmd
This file analyzes our train/test dataset, documents the label types, visualizes the number of complaints to non-complaints, and visualizes the number of each complaint category. Additionally, it runs a tf_idf analysis on the catch-all complaint category to see if another category can be identified.

### 04_build_fasttext_supervised_classifier.Rmd
This file documents the building of our fastText supervised classifier model.

### 05_define_culstering_functions.R
This file was formerly called clus_func.R. It contains the code defining a few functions. These functions will be referenced in future scripts to help build our model. One especially important function here is the avg_word_vec function.

##### Average Word Vector Function
This function will take the word vectors for each word in a tweet, and will average the vectors to create a single vector representing the tweet as a whole. The word vectors will be generated by a fasttext unsupervised model. This will effectively become a mathmatical summary of each tweet, and will be a valuable input to our model.

### 06_define_prediction_functions.R
This file was formerly called predict_func.R. It contains a lot of useful functions for our model. Two important functions defined here are the VectorizeTweet() and TweetFeatures() functions.

##### VectorizeTweet Function.
This function has two classes: one for use with a unsupervised fastText model, and another for use with a PCA model trained on the output of the VectorizeTweet() function. This class is functionally identical to the avg_word_vec() function (as far as I understand--looking at the code they should do the exact same thing, so I'm not entirely sure why we have two nearly identical functions).

The first class (used with an unsupervised fastText model) breaks a tweet down into individual words, and finds the word vectors associated with each of these words. After these word vectors are stored in a dataframe, each variable of the dataframe is averaged to produce a single vector (the same size as an individual word vector). This "tweet vector" can be thought of as a mathematical summary of the tweet.

The second class (used with a PCA model trained on the output of the first class), produces a tibble with the first n principal components of the tweet vector (where n is defined by the user).

##### TweetFeatures Function
This function creates a simple summary of a tweet's features (i.e. the number of exclamation points, the number of links used, and the number of times this user has been mentioned previously in the data).

### 07_build_classifier.Rmd
This document was formerly called classifier_construction.R. It contains the code that builds models referenced in other files, namely the model50-tweet_sample_2M_noRT.dat and xgb.modelPC4-xgb_version.dat. The xgb.modelPC4-xgb_version.dat model is the full, frankenstein model we have built. When I reference "the model," or the "frankenstein model," this is the model I am referring to.

Note: I can't seem to find the logit_classifier_func.R file anywhere. It's referenced in classifier_construction.R

### 08_define_tweet_complaint_predictor_function.R
tweet_complaint_predictor.Rmd builds a function named newTweetComplaintPredictor, which is referenced in serveral other scripts. This function uses our model to predict

### 09_classifier_testing.Rmd
This file references the full model, and makes predictions on single tweets. You can use it to see how the model will react with tweets you find online, as well as tweets you write yourself.

### 99_batch_classification.Rmd
### 99_build_standalone_fasttext_classification_model.Rmd
In this file, I create my own fastText supervised classification model to see how well it can classify on its own (i.e. without the help of a PCA and XGBoost model). This will be a good base to compare against our own xgboost model built in 07_construct_classifier.Rmd

Note: Code still has a few places it needs to be tweaked and isn't fully funcitonal yet--I need to write the .txt files and figure out how to make predictions with the trained model.

### 99_fasttext_clust_EDA.Rmd
### 99_json_parse_upload.Rmd
### 99_logit_regression_classifier.Rmd
### 99_read_tweets_json.Rmd
### 99_tweet_object.Rmd
